\section{Positions}

\vspace{6pt}

\cventry{Fall 2019 - Present}{Lecturer}{UC Berkeley EECS}{Berkeley, CA}{}{\vspace{5pt} I am primarily responsible for Computer Science 88, an introductory "CS 1" course for data science students. I share the work in many of our activities for training student instructors, including teaching our pedagogy courses and advising summer instructors.}

\vspace{6pt}

\cventry{July 2016 – Present}{Software Engineer}{Gradescope, by Turnitin}{Berkeley, CA}{}{\vspace{5pt}Gradescope is an online platform for grading written work (like exams) that allows instructors to provide detailed feedback while reducing grading time. We were a small team of less than 15 before being acquired by Turnitin in October 2018.}
    
\vspace{5pt}
    
\begin{itemize}

    \item\small{Led the development of web accessibility. Addressed technical concerns relating to compliance with WCAG 2.0 and 2.1. Set up tooling for automated front-end tests for accessibility, and trained engineers on web accessibility. Presented my web accessibility work to the Turnitin Engineering organization.}
    
    \vspace{5pt}
    
    \item\small{Led the development of growth engineering. Created modern data pipelines (hosted on Amazon Web Services) to address user onboarding and to better understand product usage.}
   
    \vspace{5pt}
   
    \item\small Collaborated with the design team on new features. Provided customer support and training on the Gradescope platform.
   
    \vspace{15pt}
\end{itemize}

\cventry{2016-2018}{Researcher and Engineer}{UC Berkeley EECS}{Berkeley, CA}{}{\vspace{5pt}Contributed to the Beauty and Joy of Computing edX course, including supporting the development of the Snap! programming language, and provided support to high school computer science teachers. (Part-time; Funded via Hopper-Dean Foundation Grant) (See "Projects".)}
    
\vspace{15pt}
