\section{Software Projects}

\vspace{6pt}

\textbf{Snap\textit{!}}\\
\small Snap\textit{!} is a blocks-based visual language designed to make teaching computer science easy, while exposing hard concepts like lambdas, recursion, and web APIs. I contribute to the core IDE, and I collaboratively designed, built and maintain the Snap\textit{!} cloud-based project infrastructure, which currently supports more than 5 million projects and over 500,000 users.
\newline
\small{\href{https://snap.berkeley.edu}{https://snap.berkeley.edu}}

\vspace{12pt}

\textbf{The Beauty and Joy of Computing}
\newline
\small BJC is a university-level non-majors or a high school level AP Computer Science Principles course designed to broaden participation in computing. In addition to programming, the course emphasizes the context and implications of computing. I provide infrastructure maintenance, technical consulting and curriculum review. I contributed curriculum heavily to early versions of the course which are still used at UC Berkeley.
\newline
\small{\href{https://bjc.berkeley.edu}{https://bjc.berkeley.edu}}

\vspace{12pt}

\textbf{Alonzo, A Staff Chatbot}

\vspace{3pt}

\small{"Alonzo" is the name of a chatbot that course staff use to automate grading processes, saving time and reducing errors. The bot has been an integral part of enabling CS10 to facilitate in-class oral lab check-offs by allowing Lab Assistants to easily enter check off data. The bot was originally started as a fun side project, but has since had multiple generations of TAs contribute to and maintain its code.}
\linebreak
\small{https://www.github.com/cs10/Alonzo}

\vspace{12pt}
\textbf{Downshift}
\newline
\small{Downshift is an open source React Component maintained by PayPal. I contribute accessibility enhancements and reviews.}
\newline
\small{\href{https://github.com/paypal/downshift}{https://github.com/paypal/downshift}}

\vspace{15pt}

