\section{Writing \& Publications}
\vspace{6pt}

\subsection{Conference and Workshop Presentations}

\vspace{5pt}

\begin{itemize}

  \setlength\itemsep{1em}
    %%%%%%%%%%% SNAPCON 2021
    \item{Snap!Con 2021 Future of Snap! Panel}
    
    \item{Snap!Con 2021 BJC Middle School Panel}

    %%%%%%%%%% TAPIA 2021
    \item{Blank, Adam; Walther, Kendra; \me; Masters-Only BOF.
    Tapia 2021
    }

    %%%%%%%%%% SIGCSE 2021
    \item{\me; TA Training PANEL}

    \item \me; Garcia, Daniel; Arvai, Eric. 2021. Effective Video Production for Online and In-Person Courses (Workshop). In Proceedings of the 52nd ACM Technical Symposium on Computer Science Education. Association for Computing Machinery, New York, NY, USA, 1349. https://doi.org/10.1145/3408877.3432509
    
    %%%%%%%%%% 2020
    \item{Snap!Con 2020 Future of Snap! Panel}
    
    %%%%%%%%% SIGCSE 2020
    \item{\me and Daniel D. Garcia. Online Learning (Talk). University of Washington CS Education Seminar, Online, 2020-05-28.}
    
    \item{\me and Daniel D. Garcia. Mastery Learning at Scale (Talk). University of Washington CS Education Seminar, Online, 2020-06-04.}
    
    \item{\me; ... TA Training PANEL}
    
    \item{Garcia, Dan; \me. 2020. Snap! v5, Our Biggest, Feature-filled Release Ever! (Demo) In Proceedings of the 51st ACM Technical Symposium on Computer Science Education (SIGCSE '20). Association for Computing Machinery, New York, NY, USA, 1417. https://doi.org/10.1145/3328778.3372549}
    
    \item{\me, Lauren Mock, Dan Garcia, Tiffany Barnes, Marnie Hill, Alexandra Milliken, Joshua Paley, Efrain Lopez, and Jason Bohrer. 2020. The Beauty and Joy of Computing Curriculum and Teacher Professional Development (Workshop). In Proceedings of the 51st ACM Technical Symposium on Computer Science Education (SIGCSE '20). Association for Computing Machinery, New York, NY, USA, 1398. https://doi.org/10.1145/3328778.3367029}

    %%%%%%%%%%%%%% 2019
    
    %%%%%%%% SnapCon! 2019
    \item{\textbf{Ball, Michael}; Jatzlau. Sven;  SnapCon! 2019 Lightning Talk: An Analysis of 500,000 Snap! Projects}
    
    \item{\textbf{Ball, Michael};  SnapCon! 2019 Lightning Talk Using JSFunction with the Wolfram Alpha API}
    
    \item{\textbf{Ball, Michael}; SnapCon! 2019 Panel 1}
    
    \item{\textbf{Ball, Michael}; SnapCon! 2019 Panel 2}
    
    \item{\textbf{Ball, Michael}; Snap\textit{!} A Look at 550K Projects. Poster. Snap!Con 2019, Heidelberg, Germany.}
    
    \item{\textbf{Ball, Michael}; SnapCon! 2019 Poster 2}
    
    \item{\textbf{Ball, Michael}; SnapCon! 2019 Poster 3}
    
    %%%%%
    
    \item{\textbf{Ball, Michael}; Romagosa, Bernat; Moenig, Jens; Harvey Brian. Snap\textit{!} A Look at 5 Years, 250,000 Users and 2 Million Projects. Poster. Proceedings of the 50th ACM Technical Symposium on Computer Science Education.}
    
    \item{Mock, Lauren; \me, Garcia, Daniel, and Barnes, Tiffany. 2019. Computer Science Principles Providers and Teachers Forum (Pre-Symposium Workshop). In Proceedings of the 50th ACM Technical Symposium on Computer Science Education (SIGCSE '19). Association for Computing Machinery, New York, NY, USA.}
    
    \item{\textbf{Ball, Michael} Teaching Accessibility Using Software. What to Teach about Accessibility SIGCSE 2019 Pre-Symposium Event.}
    
    %%%%%%%%%%%%%%%%% 2018
    \item{\textbf{Ball, Michael}. IRT in 5 Minutes: Easy Ways to Better Understand an Assessment. Lightning Talk. Proceedings of the 49th ACM Technical Symposium on Computer Science Education.} \href{http://doi.acm.org/10.1145/3159450.3162211}{http://doi.acm.org/10.1145/3159450.3162211}

    \item{Galanos, Ria; \textbf{Ball, Michael}; Dougherty, John; Hummel, Joe; Malan, David. Technology We Can't Live Without!, Revisited. Panel. Proceedings of the 49th ACM Technical Symposium on Computer Science Education.} \href{http://doi.acm.org/10.1145/3159450.3159629}{http://doi.acm.org/10.1145/3159450.3159629}

    \item{Milliken, Alexandra; \textbf{Ball, Michael}; Mock, Lauren. AP CS Principles and The Beauty and Joy of Computing Curriculum: Workshop. Proceedings of the 49th ACM Technical Symposium on Computer Science Education.} \href{http://doi.acm.org/10.1145/3159450.3162375}{http://doi.acm.org/10.1145/3159450.3162375}

    %%%%%%%%%%%%%% 2017
    
    \item{Garcia, Daniel; Harvey, Brian; Mönig, Jens; \textbf{Ball, Michael}; Romagosa, Bernat; Low, Robert; Mock, Lauren. The Beauty and Joy of Computing. Workshop. Scratch Conference 2017, Bordeaux, France, 2017-07-21.}

    \item{\textbf{Ball, Michael}; Garcia, Daniel; Mock, Lauren. Writing Autograders for Snap\textit{!} and Integrating them Into Your Course. Short Talk, Scratch Conference 2017, Bordeaux, France, 2017-07-20.}

    \item{Garcia, Daniel; Harvey, Brian; Mönig, Jens; \textbf{Ball, Michael}; Mock, Lauren; Low, Robert; Romagosa, Bernat. The Beauty and Joy of Computing and the Snap\textit{!} Programming Language. Poster. Scratch Conference 2017, Bordeaux, France, 2017-07-20.}

    \item{\textbf{Ball, Michael}; Garcia, Daniel; Mock, Lauren. Early Analysis of "In-Lab" Autograding for Snap\textit{!}. Poster. Scratch Conference 2017, Bordeaux, France, 2017-07-20.}

    \item{Mock, Lauren; \textbf{Ball, Michael}; Garcia, Daniel; Harvey, Brian. Lessons Learned Delivering a Customizable Course with Autograders to 200 Teachers. Ignite Talk. Scratch Conference 2017, Bordeaux, France, 2017-07-20.}
    
    \item{Garcia, Daniel; Romagosa, Bernat; \textbf{Ball, Michael}; Mönig, Jens; Harvey, Brian. Programming the Internet (of things) with Snap\textit{!}. Short Demo. Scratch Conference 2017, Bordeaux, France, 2017-07-19.}

    \item{\textbf{Ball, Michael}. Writing Autograders for Snap\textit{!} and Integrating Them Into Your Course. Demo. Proceedings of the 48th ACM SIGCSE Technical Symposium on Computer Science Education.} \href{http://doi.acm.org/10.1145/3017680.3022385}{http://doi.acm.org/10.1145/3017680.3022385}

    \item{\textbf{Ball, Michael}. Implementing "In-Lab" Autograding for Snap\textit{!}. Poster. Proceedings of the 48th ACM SIGCSE Technical Symposium on Computer Science Education.} \newline\href{http://doi.acm.org/10.1145/3017680.3022443}{http://doi.acm.org/10.1145/3017680.3022443}
    
    %%%%%%%%%%%%% 2016

    \item{Garcia, Daniel and \textbf{Ball, Michael}. Bringing the Beauty and Joy of Computing to the World via edX: An Experience Report. Panel. Scratch Conference 2016, Cambridge, MA, 2016-08-05.}

    \item{\textbf{Ball, Michael} and Garcia, Daniel. Autograding and Feedback for Snap\textit{!}: A Visual Programming Language. Poster. Proceedings of the 47th ACM Technical Symposium on Computing Science Education.}
    \href{http://doi.acm.org/10.1145/2839509.2850572}{http://doi.acm.org/10.1145/2839509.2850572}

    \item{Garcia, Daniel; Barnes, Tiffany; \textbf{Ball, Michael}; Biga, Emil; Paley, Josh; Hill, Marnie; Mattix, Nathan; Safa, Parisa; Morris, Sean; Kenner, Shawn. AP CS Principles and The Beauty and Joy of Computing Curriculum. Workshop. Proceedings of the 47th ACM Technical Symposium on Computing Science Education.} \href{http://doi.acm.org/10.1145/2839509.2844714}{http://doi.acm.org/10.1145/2839509.2844714}

    \item{\textbf{Ball, Michael}. Using Instant Chat for Fun and for Profit to Run a Large Class. Abstract Only. Proceedings of the 47th ACM Technical Symposium on Computing Science Education.} \href{http://doi.acm.org/10.1145/2839509.2850526}{http://doi.acm.org/10.1145/2839509.2850526}
    
    %%%%%%%% 2015

    \item{Garcia, Daniel; Harvey, Brian; Moenig, Jens; \textbf{Ball, Michael}. The Beauty and Joy of Computing. Workshop. Scratch 2015, Amsterdam, Netherlands, August 12-16, 2015.}

    \item{Garcia, Daniel; Harvey, Brian; Moenig, Jens; \textbf{Ball, Michael}. Bringing the Beauty and Joy of Computing to the World via edX. Special Session. Scratch 2015, Amsterdam, Netherlands, August 12-16, 2015.}

    \item{Garcia, Daniel; Harvey, Brian; Moenig, Jens; \textbf{Ball, Michael}. The Beauty and Joy of Computing and the Snap\textit{!} Programming Language. Poster. Scratch 2015, Amsterdam, Netherlands, August 12-16, 2015.}

    \item{\textbf{Ball, Michael}; Mock, Lauren; McKinsey, Jonathan; Machardy, Zachary; Garcia, Daniel; Titterton, Nathaniel; Harvey, Brian. Oh, Snap\textit{!} Enabling and Encouraging Success in CS1. Poster. Proceedings of the 46th ACM Technical Symposium on Computer Science Education.} \newline\href{http://doi.acm.org/10.1145/2676723.2691947}{http://doi.acm.org/10.1145/2676723.2691947}
    
    %%%%% 2014

    \item{Garcia, Daniel; \textbf{Ball, Michael}; Parikh, Aatash. L@S 2014 Demo: Best Practices for MOOC Video. Demo+Paper. Proceedings of the First ACM Conference on Learning @ Scale Conference.} \href{http://doi.acm.org/10.1145/2556325.2567889}{http://doi.acm.org/10.1145/2556325.2567889}

\end{itemize}
